### 2023-04-02 paper-reviews/papers-2023.tex
Fix typos

    \cite{IntelHTTValidation}:

@@

    Self-modifying code is supported through monitoring of writes to compiled blocks. The authors also added a DLL cache to avoid compilation overhead for subsequent runs of the same simulation. Easy to read article that would be a good reference for \herf{https://github.com/yulyugin/sim-lectures}{<<Fundamentals of Full-Platform Simulation>>} MIPT course.
\end{itemize}

>>>>

    \cite{Burns:IntelHTTValidation:2002}:

@@

    Self-modifying code is supported through monitoring of writes to compiled blocks. The authors also added a DLL cache to avoid compilation overhead for subsequent runs of the same simulation. Easy to read article that would be a good reference for \href{https://github.com/yulyugin/sim-lectures}{<<Fundamentals of Full-Platform Simulation>>} MIPT course.
\end{itemize}
